%-------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%-----FONT OPTIONS-----
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubHeader}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubHeader}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeader}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeaderListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeaderListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----Header-----


\begin{center}
    \textbf{\Huge Boming Zhang} \\ \vspace{1pt}
    \small
    Athens, GA $|$
    (+1)706-363-5179 $|$
    \href{mailto:boyanzh233@gmail.com}{boyanzh233@gmail.com} $|$
    \href{https://boyanzh.site}{\underline{boyanzh.site}} $|$
    \href{https://github.com/BoYanZh}{\underline{github.com/BoYanZh}} $|$
    \href{https://www.linkedin.com/in/bomingzh}{\underline{linkedin.com/in/bomingzh}}
\end{center}

% \vspace{-15pt}

% \vspace{-15pt}
%------EXPERIENCE------
\section{Experience}
  \resumeSubHeaderListStart
  \resumeSubHeader
    {Project Contributor}{Jul. 2024 - Present}
    {The University of Georgia, advisor Prof. Le Guan}{Athens, GA}
    \resumeItemListStart
      \resumeItem{Developing an \textbf{LLVM pass plugin} and related tools to conduct advanced fuzz testing on communication protocols such as USB and Bluetooth for ARM32 embedded devices.}
    \resumeItemListEnd
  \resumeSubHeader
    {Software Engineer (Intern, Full-Time)}{Feb. 2022 - Jul. 2022, Nov. 2022 - Jul. 2023}
    {\href{https://naivesystems.com}{Naive Systems}, advisor Xiao Jia, Kevin Sun}{Shanghai, China}
    \resumeItemListStart
      \resumeItem{Develop a static code analysis product. Implement 100+ checkers with test cases for programming specifications based on \textbf{LLVM, and CppCheck}, utilizing \textbf{syntax trees, lexical analysis, and symbolic execution}.}
      \resumeItem{Contribute to \textbf{\href{https://github.com/llvm/llvm-project/issues/60412}{LLVM}}, submitting a bug report which \textbf{reduces false-negative on 10\% translation units}.}
      \resumeItem{Build multi-process unit test scripts. Boost the test time to \textbf{25x times faster} and detect 20+ false positive cases.}
      \resumeItem{Develop a VSCode extension to read protobuf results. Implement the i18n feature with Protobuf.}
    \resumeItemListEnd

    \resumeSubHeader
      {Research \& Development Engineer Intern}{Jun. 2021 - Feb. 2022}
      {Shanghai Zhimian Weiye Technology, advisor Prof. Mian Li, Dr. Ruixiang Zheng}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Start from scratch, build a high perf. firefighting platform (Web + App) based on IoT data. Use FAHP algorithm to detect potential hazards and report \textbf{95\% less false fire alarms in milliseconds response time}.}
        \resumeItem{Deploy the system on \textbf{the fire brigade of Shanghai Province}, connected with \textbf{over 7 million IoT devices}.}
        \resumeItem{Technical leader of 2 Undergraduate \textbf{Innovation Practice Programs}, developing full-stack web \& mobile App.}
      \resumeItemListEnd

    % \resumeSubHeader
    %   {Research Assistant}{Mar. 2021 - Feb. 2022}
    %   {\href{https://sites.ji.sjtu.edu.cn/ido/}{Intelligent Design and Optimization Research Lab}, advisor Prof. Mian Li}{Shanghai, China}
    %   \resumeItemListStart
    %     \resumeItem{Develop a cryptocurrency funding rate arbitrage system in \textbf{async python} to get milli-second transaction time.}
    %   \resumeItemListEnd

    \resumeSubHeader
      {Teaching Assistant (Intro to OS, Intro to Computers and Programming)}{Fall 2020, Fall 2021}
      {Shanghai Jiao Tong University, advisor Prof. Manuel Charlemagne}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Host \textbf{exam review sessions} and \textbf{weekly lab sessions} for at most 100 students. Grade labs and homework.}
        \resumeItem{Maintain online judge test cases and multiple servers for up to 150 students as part of the FOCS student system.}
      \resumeItemListEnd

    % \resumeSubHeader
    % {Deputy Director}{Sep. 2018 - Aug. 2019}
    %   {Technology Department UM-SJTU Joint Institute Student Union, Shanghai Jiao Tong University}{Shanghai, China}
    %   \resumeItemListStart
    %     \resumeItem{Build audience interaction multimedia system using PyQt5 for welcoming parties, used by over 300 students.}
    %     \resumeItem{Hold workshops and write posts on WeChat about developing and tech every month, have in total 2k+ reads.}
    %   \resumeItemListEnd
    \resumeSubHeaderListEnd

%------PROJECTS------
% \vspace{-10pt}
\section{Projects}
    \resumeSubHeaderListStart
      \resumeProjectHeader
        {\href{https://github.com/alist-org/alist}{\textbf{AList (Github 42.3k stars)}} $|$ \emph{Golang, Go Gin, GORM, Solid.js, WebDAV, SMB, S3, FTP}}{Nov. 2022 - May. 2023}
        \resumeItemListStart
          \resumeItem{\textbf{3rd main contributor} of the project, which provides unified API and WebDAV of multiple storage protocols and cloud storage services to let the users manage their files and share resources. Implement multiple storage drivers.}
          % \resumeItem{Implement and fix multiple storage drivers, analyze protocols and packets, and fix security vulnerabilities.}
          \resumeItem{Design and implement the search feature, which is \textbf{the most highly requested feature} by users for years.}
        \resumeItemListEnd
        % {\href{https://github.com/SJTU-IPP-Firefighting}{\textbf{Intell. IoT Firefighting System}} $|$ \emph{Python3, MongoDB, Docker, React.js, React Native}}{Mar. 2021 - Feb. 2022}
      \resumeProjectHeader
        {\href{https://github.com/joint-online-judge}{\textbf{Joint Online Judge}} $|$ \emph{Python3, Golang, PostgreSQL, Redis, Docker, CGroups, React.js}}{Mar. 2021 - Present}
        \resumeItemListStart
          \resumeItem{Develop and maintain a distributed online judge system from scratch for various courses. Provide stable, secure, fast, well-documented online judge service with various integrations for \textbf{over 1000 students in the institute}.}
          \resumeItem{Build the judger's sandbox with \textbf{namespace and containerization} for isolation and accurate measurement.}
        \resumeItemListEnd
      \resumeProjectHeader
        {\href{https://gist.github.com/BoYanZh/fc4469c20fd6adf42c212114532aaac0}{\textbf{FOCS student system \& related tools}} $|$ \emph{Python3, Golang, Node.js, Docker, Nginx, Certbot}}{Nov. 2018 - Present}
        \resumeItemListStart
          \resumeItem{Develop new features and tools. Maintain the online service and software, including online judge, self-service Git, and CI platform for \textbf{over 300 students from 10 courses each term} to build, test, and grade their codes.}
          \resumeItem{Publish packages and scripts to provide CLI interface for automation. Have \textbf{200+ PyPI downloads per month}. \\}
          \resumeItem{Integrate Git service and online judge using CI platform, improve the submission speed by 4x times faster.}
        \resumeItemListEnd
    \resumeSubHeaderListEnd

%------TECHNICAL SKILLS------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
  \setlength\itemsep{0em}
    \small{
      \setlength\itemsep{0em}
      \item{
     \textbf{Languages}{: Python3, Golang, (modern) C++, C (Linux), LLVM IR, Shell, SQL, MQL, Typescript, \LaTeX} \\
     \textbf{Softwares}{: Git, Docker, Podman, PostgreSQL, MongoDB, Nginx, GitHub Actions, Drone.io, VSCode, Vim} \\
     \textbf{Frameworks}{: LLVM, FastAPI, SQLAlchemy, Go Gin, Go Fiber, GORM, Django, React.js, PyTest, NumPy} \\
    }}
 \end{itemize}

% \vspace{-10pt}
%------EDUCATION------
\section{Education}
  \resumeSubHeaderListStart
    \resumeSubHeader
      {The University of Georgia (School of Computing)}{Aug. 2023 - Present}
      {MSc in Computer Science (\textbf{GPA 3.9/4.0})}{Athens, GA}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Software Engineering (A), Privacy-Preserving Data Analysis(A), Data Mining (A).}
      \resumeItemListEnd
    \resumeSubHeader
      {Shanghai Jiao Tong University (UM-SJTU Joint Institute, ABET acred.)}{Sept. 2018 - Aug. 2022}
      {BEng in Electrical and Computer Engineering (minor in Computer Science, \textbf{GPA 4.0/4.0})}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Intro to OS (A+), Methods and Tools for Big Data (A+), Data Structures and Algo. (A)}
        \resumeItem{\textbf{2020-2021 Undergraduate Excellent Scholarship}}
        % \resumeItem{\textbf{Honors Research Program in the Undergraduate Research Course}}
        \resumeItem{Outstanding Member of Technology Department (as deputy director) UM-SJTU Joint Institute Student Union}
      \resumeItemListEnd
  \resumeSubHeaderListEnd

%----------------------
\end{document}
