%-------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%-----FONT OPTIONS-----
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubHeader}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubHeader}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeader}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeaderListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeaderListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%-----Header-----


\begin{center}
    \textbf{\Huge Boming Zhang} \\ \vspace{1pt}
    \small (+86)180-1720-9402 $|$ \href{mailto:boyanzh233@gmail.com}{\underline{boyanzh233@gmail.com}} $|$
    \href{https://boyanzh.site}{\underline{boyanzh.site}} $|$
    \href{https://github.com/BoYanZh}{\underline{github.com/BoYanZh}}
\end{center}


%------EDUCATION------
\section{Education}
  \resumeSubHeaderListStart
    \resumeSubHeader
      {Shanghai Jiao Tong University (UM-SJTU Joint Institute, ABET acred.)}{Sept. 2018 - Aug. 2022}
      {BEng in Electrical and Computer Engineering (minor in Computer Science, \textbf{GPA 4.0/4.0})}{Shanghai, China}
          \resumeItemListStart
            \resumeItem{Relevant Coursework: Intro to OS (A+), Methods and Tools for Big Data (A+), Data Structures and Algo. (A)}
            \resumeItem{\textbf{2020-2021 Undergraduate Excellent Scholarship}}
            \resumeItem{\textbf{Honors Research Program in the Undergraduate Research Course}}
            \resumeItem{Outstanding Member of Technology Department (as deputy director) UM-SJTU Joint Institute Student Union}
          \resumeItemListEnd

  \resumeSubHeaderListEnd

%------EXPERIENCE------
\section{Experience}
  \resumeSubHeaderListStart
  \resumeSubHeader
    {Software Engineer (Intern to Full-Time)}{Feb. 2022 - Jul. 2022, Nov. 2022 - Present}
    {\href{https://naivesystems.com}{Naive Systems, advisor Xiao Jia, Kevin Sun}}{Shanghai, China}
    \resumeItemListStart
      \resumeItem{Take part in a static code analysis product. Implement checkers and test cases for many programming specifications, based on \textbf{Clang Static Analyzer, LibASTMatchers, Infer, and Cppcheck}, using C++ and Golang.}
      \resumeItem{Check the correctness of the product on open source projects. Write scripts to run unit tests during CI.}
      \resumeItem{Participate in development of a VSCode extension to read results. Implement the i18n feature for checkers.}
      \resumeItem{File issues with detailed analysis on llvm project and infer with our own test cases.}
    \resumeItemListEnd

    \resumeSubHeader
      {Research \& Development Engineer Intern}{Jun. 2021 - Feb. 2022}
      {Shanghai Zhimian Weiye Technology}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Build Intell. IoT Firefighting System project. Design the architecture, and work as a full-stack developer.}
      \resumeItemListEnd

    \resumeSubHeader
      {Research Assistant}{Mar. 2021 - Feb. 2022}
      {Intelligent Design and Optimization Research Lab, advisor Prof. Mian Li}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{\textbf{Technical leader} of 2 Undergraduate Innovation Practice Programs. Build a risk control center for Shanghai Jiao Tong University School of Medicine, used by over 10 different management systems and over 100 faculties.}
        \resumeItem{Develop a cryptocurrency funding rate arbitrage system in async python to get \textbf{milli-second transaction time}.}
      \resumeItemListEnd

    \resumeSubHeader
      {Teaching Assistant (Intro to OS, Intro to Comp.)}{Sep. 2020 - Dec. 2020, Sep. 2021 - Dec. 2021}
      {Shanghai Jiao Tong University, advisor Prof. Manuel Charlemagne}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Host \textbf{exam review sessions} and \textbf{weekly lab sessions} for at most 100 students. Grade labs and homework}
        \resumeItem{Maintain online judge test cases and multiple servers for up to 150 students' usage.}
      \resumeItemListEnd

    \resumeSubHeaderListEnd

%------PROJECTS------
\section{Projects}

    \resumeSubHeaderListStart
      \resumeProjectHeader
        {\href{https://github.com/alist-org/alist}{\textbf{AList (file list program, 21k stars on Github)}} $|$ \emph{Golang, GORM, Solid.js}}{Nov. 2022 - Present}
        \resumeItemListStart
          \resumeItem{\textbf{3rd main contributor} of the project. Contribute to multiple drivers and fix security vulnerability.}
          \resumeItem{Implement the search feature. Take active part in the open source community on Github and Telegram.}
        \resumeItemListEnd
      \resumeProjectHeader
        {\href{https://github.com/joint-online-judge}{\textbf{JOJ 2.0}} $|$ \emph{Python3, Golang, PostgreSQL, Redis, LakeFS, Docker, CGroupsV1, React.js}}{Mar. 2021 - Present}
        \resumeItemListStart
          \resumeItem{Develop an online judge system from scratch for various courses. Provide stable, secure, fast, well-documented online judge service with various integrations for \textbf{over 1000 students in the institute}.}
          \resumeItem{Build the judger's sandbox with \textbf{namespace and containerization} for isolation and measurement.}
        \resumeItemListEnd
      \resumeProjectHeader
        {\href{https://github.com/SJTU-IPP-Firefighting}{\textbf{Intell. IoT Firefighting System}} $|$ \emph{Python3, MongoDB, Docker, React.js, React Native}}{Mar. 2021 - Feb. 2022}
        \resumeItemListStart
          \resumeItem{Start from scratch, build a high perf. firefighting platform (Web + App) based on IoT data. Use an algorithm to detect potential hazards and report fire alarms with high accuracy in buildings to \textbf{save life and money}.}
          \resumeItem{Deploy the system on \textbf{the fire brigade of Shanghai Province}, connected with \textbf{over 7 million IoT devices}.}
        \resumeItemListEnd
      \resumeProjectHeader
        {\href{https://gist.github.com/BoYanZh/fc4469c20fd6adf42c212114532aaac0}{\textbf{FOCS student system \& related tools}} $|$ \emph{Python3, Golang, Node.js, Docker, Nginx, Certbot}}{Nov. 2018 - Present}
        \resumeItemListStart
          \resumeItem{Develop new features and maintain the online service and software, including online judge, self-service Git platform, CI platform for \textbf{over 300 students from 10 courses each term} to build, test, and grade their codes.}
          \resumeItem{Build various tools to connect Canvas LMS, Online Judge, and Gitea together. Get \textbf{in total 60+ stars} on Github.}
        \resumeItemListEnd
    \resumeSubHeaderListEnd


%
%------TECHNICAL SKILLS------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python3, Golang, (modern) C++, C (Linux), Typescript, Shell, \LaTeX} \\
     \textbf{Frameworks}{: FastAPI, SQLAlchemy, Gin, Fiber, GORM, Django, React.js, PyTest, NumPy} \\
     \textbf{Developer Tools}{: Git, Docker, Podman, Github Actions, Drone.io, VSCode, Pre-commit} \\
    }}
 \end{itemize}


%----------------------
\end{document}
