%-------------
% Resume in Latex
% Author : Sidratul Muntaha Ahmed
% License : MIT
%------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{hyperref}
% \hypersetup{
%     colorlinks=true,
%     linkcolor=[rgb]{0.6,0,0.6},
%     filecolor=[rgb]{0.6,0,0.6},
%     urlcolor=[rgb]{0.6,0,0.6},
%     citecolor=[rgb]{0.6,0,0.6}
% }
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=blue,
    urlcolor=blue,
    citecolor=blue,
}

%-----FONT OPTIONS-----
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-6pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubHeader}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.98\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubHeader}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeader}[2]{
    \item
    \begin{tabular*}{0.98\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeaderListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeaderListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%----------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

\begin{center}
    \textbf{\Huge Boming Zhang} \\ \vspace{1pt}
    \small
    Athens, GA $|$
    (+1)706-363-5179 $|$
    \href{mailto:boyanzh233@gmail.com}{boyanzh233@gmail.com} $|$
    \href{https://boyanzh.site}{boyanzh.site} $|$
    \href{https://github.com/BoYanZh}{github.com/BoYanZh} $|$
    \href{https://www.linkedin.com/in/bomingzh}{linkedin.com/in/bomingzh}
\end{center}

\section{Experience}
  \resumeSubHeaderListStart
  \resumeSubHeader
    {Project Contributor}{Jul. 2024 - Present}
    {The University of Georgia, advisor \href{https://guanle.org/}{Prof. Le Guan}}{Athens, GA}
    \resumeItemListStart
      \resumeItem{Developing an \textbf{LLVM pass plugin}, manipulating IR, for advanced fuzz testing on embeded device protocols.}
    \resumeItemListEnd
  \resumeSubHeader
    {Software Engineer (Intern, Full-Time)}{Feb. 2022 - Jul. 2022, Nov. 2022 - Jul. 2023}
    {\href{https://naivesystems.com}{Naive Systems}, advisor Xiao Jia, Kevin Sun}{Shanghai, China}
    \resumeItemListStart
      \resumeItem{Developed a static code analysis product using \textbf{LLVM}, focusing on system-level programming specifications. Implemented \href{https://github.com/naivesystems/analyze}{100+ checkers} utilizing \textbf{syntax trees, lexical analysis, symbolic execution} for code analysis.}
      \resumeItem{Contributed to \textbf{LLVM}, submitting a \href{https://github.com/llvm/llvm-project/issues/60412}{bug report} that reduced false-negatives by 10\% in translation units.}
      \resumeItem{Optimized multi-process unit testing, achieving a \textbf{25x speedup} in test execution time.}
    \resumeItemListEnd

  \resumeSubHeader
    {Full Stack Development Engineer Intern}{Jun. 2021 - Feb. 2022}
    {Shanghai Zhimian Weiye Technology, advisor \href{https://sites.ji.sjtu.edu.cn/ido/professor/}{Prof. Mian Li}, Dr. Ruixiang Zheng}{Shanghai, China}
    \resumeItemListStart
      \resumeItem{Start from scratch, built \href{https://github.com/SJTU-IPP-Firefighting}{a high perfermance firefighting platform (Web + App)} based on IoT data. Used FAHP algorithm to detect potential hazards and report \textbf{95\% less false fire alarms} in \textbf{milliseconds response time}.}
      \resumeItem{Scaled the system to handle data from \textbf{over 7 million IoT devices}, while keeping high availability.}
      \resumeItem{Deployed the system on \textbf{the fire brigade of Shanghai Province}.}
    \resumeItemListEnd

  \resumeSubHeader
    {Teaching Assistant (\href{https://www.ji.sjtu.edu.cn/academics/courses/courses-by-number/course-info/?id=444}{Intro to OS}, \href{https://www.ji.sjtu.edu.cn/academics/courses/courses-by-number/course-info/?id=74}{Intro to Computers and Programming})}{Fall 2020, Fall 2021}
    {Shanghai Jiao Tong University, advisor \href{https://www.ji.sjtu.edu.cn/about/faculty-staff/faculty-directory/faculty-detail/76/}{Prof. Manuel Charlemagne}}{Shanghai, China}
    \resumeItemListStart
      \resumeItem{Conducted weekly lab sessions on operating systems concepts, including process management, memory allocation.}
      % \resumeItem{Maintain online judge test cases and multiple servers for up to 150 students as part of the FOCS student system.}
      \resumeItem{Resolved 200+ technical issues through office hours and online support channels.}
    \resumeItemListEnd
  \resumeSubHeaderListEnd

\section{Projects}
    \resumeSubHeaderListStart
      \resumeProjectHeader
        {\href{https://github.com/joint-online-judge}{\textbf{Joint Online Judge}} $|$ \emph{Python3, Golang, PostgreSQL, Redis, Grafana, Docker, React.js}}{Mar. 2021 - Present}
        \resumeItemListStart
          \resumeItem{\textbf{Led a team of 6 undergraduate students} to develop and maintain a distributed online judge system based on Gitea Actions. Provide online judge service for \textbf{1000+ students} and \textbf{10000+ submissions monthly}.}
          \resumeItem{Built secure sandbox using \textbf{Linux namespaces and containerization} for process isolation.}
          \resumeItem{Established workflows, coordinated feature implementations, and mentored team members on system design.}
        \resumeItemListEnd
      \resumeProjectHeader
        {\textbf{\href{https://github.com/alist-org/alist}{AList} (Github 42.3k stars)} $|$ \emph{Golang, Go Gin, GORM, Solid.js, WebDAV, SMB, S3, FTP}}{Nov. 2022 - May. 2023}
        \resumeItemListStart
          \resumeItem{\textbf{3rd main contributor}, focusing on implementing and optimizing \textbf{storage drivers for various protocols}.}
          \resumeItem{Designed and implemented a high-performance search feature, handling large-scale virtual file systems efficiently.}
          \resumeItem{Analyzed low-level protocols and network packets to improve system performance and security.}
        \resumeItemListEnd
      \resumeProjectHeader
        {\href{https://gist.github.com/BoYanZh/fc4469c20fd6adf42c212114532aaac0}{\textbf{FOCS student system}} $|$ \emph{Python3, Golang, Node.js, Docker, Nginx}}{Nov. 2018 - Present}
        \resumeItemListStart
          \resumeItem{Maintained a comprehensive academic platform including online judge, Git service with CI platform for \textbf{over 300 students from 10 courses each term} to build, test, and grade their codes.}
          \resumeItem{Improving Git service and online judge integration with CI platform and scripts for 4x faster submissions.}
          \resumeItem{Developed CLI tools for system automation, garnering 200+ monthly downloads on PyPI.}
          \resumeItem{Improved system uptime to 99.99\% by implementing automated health checks and failover mechanisms.}
        \resumeItemListEnd
    \resumeSubHeaderListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{
      \item{
     \textbf{Languages}{: Python3, Golang, C, (modern) C++, LLVM IR, JavaScript, Assembly, Shell, SQL} \\
     \textbf{Systems \& Tools}{: Linux, Git, Docker, LLVM, GDB, Valgrind, Wireshark, Ghidra, GNU Make, CMake, perf} \\
     \textbf{Frameworks \& Libraries}{: Django, FastAPI, SQLAlchemy, Go Gin, Go Fiber, GORM, React.js, Protocol Buffers} \\
     \textbf{Databases \& Services}{: PostgreSQL, MongoDB, Redis, Nginx, GitHub Actions, Grafana, Drone.io, Jenkins}
    }}
 \end{itemize}

\section{Education}
  \resumeSubHeaderListStart
    \resumeSubHeader
      {The University of Georgia (School of Computing)}{Aug. 2023 - Present}
      {MSc in Computer Science (\textbf{GPA 3.9/4.0})}{Athens, GA}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Software Engineering (A), Privacy-Preserving Data Analysis (A), Data Mining (A)}
      \resumeItemListEnd
    \resumeSubHeader
      {Shanghai Jiao Tong University (UM-SJTU Joint Institute, ABET acred.)}{Sept. 2018 - Aug. 2022}
      {BEng in Electrical and Computer Engineering (minor in Computer Science, \textbf{GPA 4.0/4.0})}{Shanghai, China}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Operating Systems (A+), Computer Architecture (A), Data Structures and Algorithms (A)}
        \resumeItem{\textbf{2020-2021 Undergraduate Excellent Scholarship}}
      \resumeItemListEnd
  \resumeSubHeaderListEnd

\end{document}
